Introduction: a pipeline to analyse time-course gene expression data

### 2019-05-08 scripts/00_introduction.Rmd
Better fig1
Preparing for switch to pdf format

---
title: "Introduction: a pipeline to analyse time-course gene expression data"
output: rmarkdown::html_vignette
bibliography: bibliography.bib
---

@@

- Add legends to the plots that don't have.
- Currently have two functions "plot_genes", "plot_centroids", that do exactly
  the same thing. Find a better name for both of them
- On the schema plot, replace clustering schemas with something else.

@@

```{r schema, echo=FALSE, fig.width=8, fig.cap="Workflow for analyzing time-course datasets."}
library(knitr)
knitr::include_graphics("images/fig1_schemas.png")
```

>>>>

---
title: "Introduction: a pipeline to analyse time-course gene expression data"
author:
    - name: Nelle Varoquaux
      affiliation: Department of Statistics and Berkeley Institute for Data Science, University of California, Berkeley, Berkeley, CA
    - name: Elizabeth Purdom
      affiliation: Department of Statistics, University of California, Berkeley, Berkeley, CA
keywords: >
    time-course gene expression data, clustering, time-course
    differential expression analysis, workflow
vignette: >
    %\VignetteIndexEntry{A worfklow for low-level analyses of scRNA-seq data}
    %\VignetteEngine{knitr::rmarkdown}
output: rmarkdown::html_vignette

bibliography: bibliography.bib
---

@@

- Add legends to the plots that don't have.
- Currently have two functions "plot_genes", "plot_centroids", that do exactly
  the same thing. Find a better name for both of them

@@

```{r schema, echo=FALSE, fig.width=8, fig.cap="Workflow for analyzing time-course datasets."}
library(BiocStyle)
library(knitr)
knitr::include_graphics("images/fig1_schemas.png")
```
